Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-06-18 Ben_Manuscripts/structure_paper/Draft.tex
Figure updates

% BJC5 : This is how it is described in Xunda's papers. Should I shift to something
% that doesn't rely on stacked disks? Maybe illustrate monomers stacked into
% columns instead?
% BJC6 : I will get to redo-ing this. Just takes some time to refamiliarize myself with
% the software I used to create it
%MRS8: sound good.
  \begin{figure}
	\centering
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{NaGA3C11.eps}
		\caption{}~\label{fig:monomer}
	\end{subfigure}
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{monomer_twocolor.png}
		\caption{}~\label{fig:atomistic_monomer}
	\end{subfigure}
	\begin{subfigure}{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{wedge_thick.png}
		\caption{}~\label{fig:wedge}
	\end{subfigure}
		\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{layer_thick.png}
		\caption{}~\label{fig:wedge_layer}
	\end{subfigure}
	\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{hexagonal_packing.png}
		\caption{}~\label{fig:hex_packing_simple}
	\end{subfigure}
	\caption{The LLC monomer Na-GA3C11 (a) rendered atomistically (b)
	exhibits wedge-like character (c). Monomer wedges assemble into disks (d) with
	hydrophilic head groups (blue) facing towards the disk center. The disks
	assemble into hexagonally packed columnar mesophases (e).}~\label{fig:assembly}
  \end{figure}

@@

  \begin{figure}[!htb]
        \centering
        \begin{subfigure}[t]{0.43\linewidth}
                \centering
                \includegraphics[width=\linewidth]{SAXS.png}
                \caption{}\label{fig:SAXS}
        \end{subfigure}
        \begin{subfigure}[t]{0.47\linewidth}
                \centering
                \includegraphics[width=\linewidth]{WAXS_annotated_words.png} 
                \caption{}\label{fig:WAXS}
        \end{subfigure}
	\caption{(a) (Reproduced from \citenum{feng_thin_2016}) The repeat spacing
		in the 1D small angle X-ray scattering pattern is characteristic of hexagonal
		packing. The leading peak, q*, represents the distance between the
		d\textsubscript{100} planes. Using this distance, we know that the distance
		between pore centers is 4.12 nm. (b) 2D WAXS gives
		details about repeating features on the order of angstroms. Experimentalists
		have explained each of the 5 major reflections present as follows: (R-$\pi$) Aromatic
		head groups $\pi-\pi$ stack 3.7 \AA~apart. (R-double) Monomers arrange vertically in
		a 2\textsubscript{1} helix. (R-alkanes) Alkane chain tails pack 4.5 \AA~apart. (R-spots)
		Monomer tails are tilted with respect to the membrane plane. (V) As derived from
		SAXS, the pores are spaced 4.12 nm apart and pack hexagonally}
	\label{fig:SWAXS}
 \end{figure}

@@

  We generated an ensemble of characteristic, low-energy vacuum monomer
  configurations by applying a simulated annealing process to a
  parameterized monomer. We cooled monomers from 1000K to 50K over 10
  nanoseconds. We randomly pulled a low energy configuration from the
  trajectory then reassigned charges using \texttt{molcharge}. Using the new
  charges, we annealed the monomer system again and pulled a random monomer
  configuration from the trajectory which we used for full system
  construction (Figure~\ref{fig:python}a). See section S-\ref{S-section:parameterization} 
  for further detail of the parameterization process.

@@

  The timescale for self-assembly of monomers into the hexagonal phase is
  unknown and likely outside of a reasonable length for an atomistic simulation,
  calling for a more efficient way to build the system. Previous work has shown
  a coarse-grained model self assemble into the H\textsubscript{II} phase
  configuration in $\sim$1000 ns \cite{mondal_self-assembly_2013}.  We
  attempted atomistic self-assembly by packing monomers into a box using Packmol
  \cite{martinez_packmol:_2009}. Simulations of greater than 100 ns show no
  indicators of progress towards an ordered system (see section S-\ref{S-section:self_assembly}). 
  To bypass the slow self-assembly process, we use Python scripts to assemble monomers
  into a structure close to one of a number of hypothesized equilibrium configurations
  (Figure~\ref{fig:python}).

  % BJC5: This needs to be modified to reflect columnar build procedure
  \begin{figure}
	\centering
	\includegraphics[width=0.75\linewidth]{build.PNG} %BJC: put an xyz axis with the unit cell
	\caption{(a) We parameterized a single monomer and annealed it to produce a low energy
		configuration. (b) A Python script assembles monomers into columns which are duplicated 
		and rotated to surround hydrophilic pore centers. (c) We chose to stack twenty monomers
		into each column. (d) The pores are duplicated and placed into a monoclinic unit cell.}\label{fig:python}
  \end{figure}

@@

  We calculated ionic conductivity using the Nernst-Einstein relationship, which 
  relates the DC ionic conductivity, $\sigma$, to ion diffusivity, $D$, 
  concentration, $C$, ion charge, $q$, the Boltzmann constant, $k_b$, and 
  temperature, $T$: 
  \begin{equation}
	\sigma = \dfrac{q^2CD}{k_b T} 
	\label{eqn:nernst_einstein}
  \end{equation}
  We measured sodium ion diffusion coefficients by calculating the slope
  of the linear region of the z-direction mean square displacement curve as
  indicated by the Einstein relation \cite{einstein_investigations_1956}. We
  visualized the MSD plot to determine where to begin and end a linear fit. We
  measured ion concentration with respect to the volume of the entire unit cell. 
  More details are provided in the Supporting Information, Section~S-\ref{section:ionic_conductivity}.

>>>>

  \begin{figure}
	\centering
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{NaGA3C11.eps}
		\caption{}~\label{fig:monomer}
	\end{subfigure}
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{monomer_twocolor.png}
		\caption{}~\label{fig:atomistic_monomer}
	\end{subfigure}
	\begin{subfigure}{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{wedge_thick.png}
		\caption{}~\label{fig:wedge}
	\end{subfigure}
		\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{columns.png}
		\caption{}~\label{fig:wedge_layer}
	\end{subfigure}
	\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{hexagonal_packing.png}
		\caption{}~\label{fig:hex_packing_simple}
	\end{subfigure}
	\caption{(a) The LLC monomer Na-GA3C11 (b) rendered atomistically (c)
	exhibits wedge-like character. (d) Monomers stack on top of each other with
	short range order and assemble into pores. (e) The hydrophilic head groups 
	(blue) facing towards the pore center. The pores assemble into hexagonally
	packed columnar mesophases.}~\label{fig:assembly}
  \end{figure}

@@

  \begin{figure}[!htb]
        \centering
        \begin{subfigure}[t]{0.405\linewidth}
                \centering
                \includegraphics[width=\linewidth]{SAXS.png}
                \caption{}\label{fig:SAXS}
        \end{subfigure}
        \begin{subfigure}[t]{0.495\linewidth}
                \centering
                \includegraphics[width=\linewidth]{WAXS_annotated_words.png} 
                \caption{}\label{fig:WAXS}
        \end{subfigure}
	\caption{(a) (Reproduced from \citenum{feng_thin_2016}) The repeat spacing
		in the 1D small angle X-ray scattering pattern is characteristic of hexagonal
		packing. The leading peak, q*, represents the distance between the
		d\textsubscript{100} planes. Using this distance, we know that the distance
		between pore centers is 4.12 nm. (b) 2D WAXS gives
		details about repeating features on the order of angstroms. Experimentalists
		have explained each of the 5 major reflections present as follows: (R-$\pi$) Aromatic
		head groups $\pi-\pi$ stack 3.7 \AA~apart. (R-double) Monomers arrange vertically in
		a 2\textsubscript{1} helix. (R-alkanes) Alkane chain tails pack 4.5 \AA~apart. (R-spots)
		Monomer tails are tilted with respect to the membrane plane. (V) As derived from
		SAXS, the pores are spaced 4.12 nm apart and pack hexagonally}
	\label{fig:SWAXS}
 \end{figure}

@@

  We generated an ensemble of characteristic, low-energy vacuum monomer
  configurations by applying a simulated annealing process to a
  parameterized monomer. We cooled monomers from 1000K to 50K over 10
  nanoseconds. We randomly pulled a low energy configuration from the
  trajectory then reassigned charges using \texttt{molcharge}. Using the new
  charges, we annealed the monomer system again and pulled a random monomer
  configuration from the trajectory which we used for full system
  construction (Figure~\ref{fig:build_procedure}a). See section S-\ref{S-section:parameterization} 
  for further detail of the parameterization process.

@@

  The timescale for self-assembly of monomers into the hexagonal phase is
  unknown and likely outside of a reasonable length for an atomistic simulation,
  calling for a more efficient way to build the system. Previous work has shown
  a coarse-grained model self assemble into the H\textsubscript{II} phase
  configuration in $\sim$1000 ns \cite{mondal_self-assembly_2013}.  We
  attempted atomistic self-assembly by packing monomers into a box using Packmol
  \cite{martinez_packmol:_2009}. Simulations of greater than 100 ns show no
  indicators of progress towards an ordered system (see section S-\ref{S-section:self_assembly}). 
  To bypass the slow self-assembly process, we use Python scripts to assemble monomers
  into a structure close to one of a number of hypothesized equilibrium configurations
  (Figure~\ref{fig:build_procedure}).

  % BJC5: This needs to be modified to reflect columnar build procedure
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
  \includegraphics[width=\linewidth]{monomer_diagonal.png}
  \caption{}
  \end{subfigure}
  \begin{subfigure}[t]{0.42\textwidth}
  \includegraphics[width=\linewidth]{stacked_monomers.png}
  \caption{}
  \end{subfigure}
  \begin{subfigure}[t]{0.35\textwidth}
  \includegraphics[width=\linewidth]{initial_pore.png}
  \caption{}
  \end{subfigure}
  \begin{subfigure}[t]{0.45\textwidth}
  \includegraphics[width=\linewidth]{initial_unit_cell.png}
  \caption{}
  \end{subfigure}
  \caption{(a) We parameterized a single monomer and annealed it to produce a low energy
		configuration. (b) We assembled monomers into columns by stacking them on top of each 
		other. (c) We duplicated each column and rotated them to create hydrophilic pore centers.
		We chose to stack twenty monomers into each column. (d) We duplicated the pores and 
		placed them into a monoclinic unit cell.}\label{fig:build_procedure}
  \end{figure}

  %BJC7: old
%  \begin{figure}
%	\centering
%	\includegraphics[width=0.75\linewidth]{build.PNG} %BJC: put an xyz axis with the unit cell
%	\caption{(a) We parameterized a single monomer and annealed it to produce a low energy
%		configuration. (b) A Python script assembles monomers into columns which are duplicated 
%		and rotated to surround hydrophilic pore centers. (c) We chose to stack twenty monomers
%		into each column. (d) The pores are duplicated and placed into a monoclinic unit cell.}\label{fig:python}
%  \end{figure}

@@

  We calculated ionic conductivity using the Nernst-Einstein relationship, which 
  relates the DC ionic conductivity, $\sigma$, to ion diffusivity, $D$, 
  concentration, $C$, ion charge, $q$, the Boltzmann constant, $k_b$, and 
  temperature, $T$: 
  \begin{equation}
	\sigma = \dfrac{q^2CD}{k_b T} 
	\label{eqn:nernst_einstein}
  \end{equation}
  We measured sodium ion diffusion coefficients by calculating the slope
  of the linear region of the z-direction mean square displacement curve as
  indicated by the Einstein relation \cite{einstein_investigations_1956}. We
  visualized the MSD plot to determine where to begin and end a linear fit. We
  measured ion concentration with respect to the volume of the entire unit cell. 
  More details are provided in the Supporting Information, Section~S-\ref{S-section:ionic_conductivity}.
